%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[11pt]{article}
\usepackage[a4paper, left=0.8in, right=0.8in, top=0.8in, bottom=0.8in]{geometry}

\newcommand{\DERSKILLS}{mathematical and statistical techniques for problem solving}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}
\usepackage{multicol}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% \addtolength{\oddsidemargin}{-0.6in}
% \addtolength{\evensidemargin}{-0.5in}
% \addtolength{\textwidth}{1.19in}
% \addtolength{\topmargin}{-.7in}
% \addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{2pt}} % was -2pt
  }
}
\newcommand{\resumeSubheading}[4]{
  \vspace{2pt}\item % was -2pt
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small#3} & \textbf{\small #2} \\
      \textit{#1} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt} % was -7pt
}

\newcommand{\NewSubheading}[2]{
  \vspace{2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{2pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{center}
    {\Huge \scshape Ankit  Singh} \\ \vspace{1pt}
    High Wycombe, Buckinghamshire, United Kingdom \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +44-7470-354-634 ~ \textbf{Email}: \href{mailto:singhank.astro@gmail.com}{\underline{singhank.astro@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/ankit-singh-09529997/}{\textbf{LinkedIn}: \underline{ankit-singh-09529997}} ~
    \href{https://github.com/ansingh16}{\textbf{GitHub}: \underline{ansingh16}}
    \vspace{-8pt}
\end{center}

\section*{Summary}
PhD in Physics with 4+ years of postdoctoral research applying advanced statistical modeling, simulations, and data analytics to large-scale datasets. Strong Python and SQL developer with hands-on experience in time series forecasting, clustering, classification, and portfolio analytics. Completed two applied AI and data science programs from WorldQuant University, covering projects in computer vision, A/B testing, and financial modeling. Actively seeking data science roles to apply my analytical skills to real-world problems. Full UK work rights.

\section*{Skills}
\vspace{-4pt}
\begin{tabularx}{\textwidth}{@{} l @{\hspace{10pt}} X @{}}
\textbf{Modeling:} & Linear/Logistic Regression, Decision Trees, Random Forests, ARIMA, GARCH, CNNs, YOLOv8, GANs, K-Means, PCA \\
\textbf{Deployment:} & Streamlit, Flask, GitHub, Dash, ETL Pipelines \\
\textbf{Visualization:} & Matplotlib, Seaborn, Plotly, Dashboards \\
\textbf{Programming:} & Python (NumPy, Pandas, Scikit-learn, PyTorch), SQL, MPI, OpenMP \\
\textbf{Tools \& Platforms:} & Git, Jupyter, Linux, MongoDB, LaTeX \\
\textbf{Domain Knowledge:} & Financial Markets, Forecasting, Risk Modeling, Computer Vision \\
\end{tabularx}

\section{Experience}
\resumeSubHeadingListStart

\NewSubheading{Quantitative Finance Projects}{}
\resumeItemListStart
\resumeItem{\textbf{Option Pricing Models:} Implemented Binomial Tree, Black-Scholes, and Monte Carlo simulations for derivatives pricing. \href{https://github.com/ansingh16/derivative_pricing.git}{\underline{GitHub}}}
\resumeItem{\textbf{Backtesting Framework:} Developed an OOP-based simulation for stock trading strategies. Incorporated volatility-adjusted signals using GARCH. \href{https://github.com/ansingh16/Backtesting}{\underline{GitHub}}}
\resumeItem{\textbf{Portfolio Optimization:} Applied Modern Portfolio Theory, Monte Carlo simulations, and convex optimization to model efficient frontiers. \href{https://github.com/ansingh16/portfolio-optimization}{\underline{GitHub}}}
\resumeItem{\textbf{Risk Management Toolkit:} Created technical indicator functions, Sharpe/Alpha/Beta calculators, and VaR estimators with signal denoising filters. \href{https://github.com/ansingh16/risk-management}{\underline{GitHub}}}
\resumeItem{\textbf{Time Series Forecasting:} Modeled equity prices using ARIMA and GARCH, with rolling window predictions and diagnostic dashboards. \href{https://github.com/ansingh16/Time_Series_Analysis}{\underline{GitHub}}}
\resumeItem{\textbf{Mutual Fund Analyzer:} Built a Streamlit app integrating public APIs to assess diversification, Sharpe ratio, and sector exposure. \href{https://mf-analysis.streamlit.app/}{\underline{App}} \href{https://github.com/ansingh16/MF_analysis}{\underline{GitHub}}}
\resumeItemListEnd

\resumeSubheading
{Korea Institute for Advanced Study (KIAS)}{November 2020 -- November 2024}
{Research Fellow}{Seoul, Republic of Korea}
\resumeItemListStart
\resumeItem{Led data-centric research using statistical models on large-scale astrophysical data. Designed Python pipelines for cleaning, merging, and feature extraction, significantly reducing analysis time by 80\% resulting in four peer-reviewed publications.}
\resumeItem{Designed a feature extraction and postprocessing pipeline, creating a novel dataset that reduced processing time by 30\%. Published 5 peer-reviewed papers based on this work.}
\resumeItemListEnd

\resumeSubheading
{Indian Institute for Science Education and Research (IISER)}{Aug 2014 -- Aug 2020}
{Ph.D. Research}{Mohali, India}
\resumeItemListStart
\resumeItem{Used SQL and clustering algorithms for astrophysical data analysis, resulting in two peer-reviewed publications.}
\resumeItem{Developed a novel mock data generation technique, improving statistical significance tenfold. Published 4 peer-reviewed papers during PhD.}
\resumeItemListEnd

\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Indian Institute for Science Education and Research (IISER) Mohali}{Aug 2014 -- Aug 2020}
{Ph.D. in Physics}{Mohali, India}
\resumeSubheading
{Department of Physics and Astrophysics, University of Delhi}{Aug 2012 -- May 2014}
{M.Sc. in Physics}{New Delhi, India}
\resumeSubHeadingListEnd

\section{Certifications}
\resumeSubHeadingListStart
\resumeSubheading
{Applied AI Lab – Deep Learning for Computer Vision}{July 2025}
{WorldQuant University (Remote)}{}
\resumeItemListStart
\resumeItem{Completed six end-to-end projects in image classification, object detection (YOLOv8), GAN-based image generation, and facial recognition.}
\resumeItem{Technologies: PyTorch, OpenCV, HuggingFace Transformers \& Diffusers, Flask, Streamlit, Stable Diffusion.}
\resumeItem{Built and deployed web apps for wildlife detection, crop disease classification, traffic monitoring, celebrity face recognition, medical image generation, and meme creation.}
\resumeItemListEnd

\resumeSubheading
{Applied Data Science Program}{July 2025}
{WorldQuant University (Remote)}{}
\resumeItemListStart
\resumeItem{Completed eight projects spanning regression, classification, clustering, time series forecasting, A/B testing, and volatility modeling.}
\resumeItem{Technologies: Python, Pandas, Scikit-learn, SQL, MongoDB, Plotly Dash, GARCH, ARIMA, SQLite, Linux.}
\resumeItem{Built predictive models (Linear, Logistic, Decision Tree, Random Forest, Gradient Boosting, GARCH, K-Means) and deployed dashboards for data-driven insights.}
\resumeItem{Designed ETL pipelines, implemented API calls, conducted chi-square hypothesis tests, and deployed interactive applications.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Achievements}
\resumeItemListStart
\resumeItem{9 peer-reviewed publications (4 during PhD, 5 during postdoc) with 100+ citations.}
\resumeItem{Awarded Certificate of Merit (Top 1\% nationwide) in Indian Science Examination, 2007.}
\resumeItem{Received 5 competitive international travel and research grants.}
\resumeItemListEnd

\section{Leadership \& Involvement}
\resumeItemListStart
\resumeItem{Team Lead: Maintained research group website for 4 years. Coordinated collaboration meetings across time zones.}
\resumeItem{Organised 4 international conferences. Taught and assisted in 7 university courses.}
\resumeItem{Led 5 public outreach events promoting science and astronomy.}
\resumeItemListEnd

\end{document}
